---
title: "Day 1 Interactive Session 2"
author: "Peter Menzies"
date: "8/2/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
```


### Logs and Exponents in R

Some examples of using the `log()` function and `exp()` function in R

```{r}
# examples of logarithms

log(4)

exp(1.386294)

exp(1)

log(exp(1))

```

### Creating Sequences of Values

```{r}

# a sequence of 1 - 20, by 1

ex_1 <- seq(from = 1, to = 20, by = 1)

# vector from 0 to 40 by incr of 0.2

ex_2 <- seq(from = 0, to = 40, by = 0.2)
```

### Create a function for logistic growth

Given the carrying capacity, initial population, growth rate, and time, use the logistic growth model to estimate the population at that time.

```{r}
pop_logistic <- function(capacity, init_pop, rate, time_yr) {
  
  capacity / (1 + ((capacity - init_pop) / init_pop) * exp(-rate * time_yr))
  
  
}

pop_logistic(capacity = 2580, init_pop = 230, rate = 0.32, time_yr = 2.4)
```

### Finding pop over a sequence of values

```{r}
time_vec <- seq(from = 0, to = 20, by = 0.5)

time_vec
```
Now let's est the pop over that range of times, given capacity - 2580, init pop = 230, rate - 0.32

```{r}
chipmunk_pop <- pop_logistic(capacity = 2580, init_pop = 230, rate = 0.32, time_yr = time_vec)
```

### Create a data frame and plot a chipmunk pop overt time

```{r}

chipmunk_df <- data.frame(time_vec, chipmunk_pop)
```

### Create a bare min ggplot graph

```{r}
ggplot(data = chipmunk_df, aes(x = time_vec, y = chipmunk_pop)) + 
  geom_point() +
  labs(x = "Time (years)",
       y = "Chipmunk Population (individuals)",
       title = "Inyo NF Chipmunks",
       subtitle = "Subtitle")
```


